\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{University of Queensland} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Epistasis follow-up \\[0.3cm] \huge *** summary *** \\ \horrule{2pt} \\[0.5cm] \date{}

### 2015-04-28 investigation/docs/overview.tex
edits to the .tex file. needs re-comiling on desktop
data sig files added , report updated (again)

\documentclass[paper=a4, fontsize=11pt]{scrartcl}         % Article class of KOMA-script with 11pt font and a4 format
\usepackage[T1]{fontenc}
\usepackage{fourier}
\usepackage{float}
\usepackage{placeins}
\usepackage[english]{babel}                     % English language/hyphenation
\usepackage[protrusion=true,expansion=true]{microtype}        % Better typography
\usepackage{amsmath,amsfonts,amsthm}                % Math packages
\usepackage[pdftex]{graphicx}                   % Enable pdflatex
\usepackage{url}
\usepackage{multicol}
\usepackage{lscape}
\usepackage{parskip}

@@

\begin{table}[ht]
\centering
\begin{tabular}{llllllll}
  \hline
 gene & probename & snp1 & snp2 & filter & gene.1 & nthreshold & P\_emp \\ 
  \hline
ADK & ILMN\_2358626 & rs2395095 & rs10824092 & 1 & ADK & 3 & 7.74 \\ 
ATP13A1 & ILMN\_2134224 & rs4284750 & rs873870 & 2 & ATP13A1 & 23 & 7.08 \\ 
C21ORF57 & ILMN\_1795836 & rs9978658 & rs11701361 & 2 & C21ORF57 & 6 & 5.65 \\ 
CSTB & ILMN\_1761797 & rs9979356 & rs3761385 & 2 & CSTB & 4 & 7.51 \\ 
CTSC & ILMN\_2242463 & rs7930237 & rs556895 & 1 & CTSC & 1 & 5.59 \\ 
FN3KRP & ILMN\_1652333 & rs898095 & rs9892064 & 2 & FN3KRP & 7 & 6.77 \\ 
GAA & ILMN\_2410783 & rs11150847 & rs12602462 & 2 & GAA & 9 & 6.91 \\ 
HNRPH1 & ILMN\_2101920 & rs6894268 & rs4700810 & 2 & HNRPH1 & 13 & 7.14 \\ 
LAX1 & ILMN\_1769782 & rs1891432 & rs10900520 & 2 & LAX1 & 5 & 6.64 \\ 
MBLN1 & ILMN\_2313158 & rs11981513 & rs13069559 & 1 & MBNL1 & 86 & 9.06 \\ 
MBLN1 & ILMN\_2313158 & rs16864367 & rs13079208 & 2 & MBNL1 & 79 & 7.22 \\ 
MBLN1 & ILMN\_2313158 & rs2030926 & rs13069559 & 1 & MBNL1 & 91 & 9.06 \\ 
MBLN1 & ILMN\_2313158 & rs218671 & rs13069559 & 1 & MBNL1 & 98 & 9.06 \\ 
MBLN1 & ILMN\_2313158 & rs2614467 & rs13069559 & 1 & MBNL1 & 95 & 9.06 \\ 
MBLN1 & ILMN\_2313158 & rs7710738 & rs13069559 & 1 & MBNL1 & 89 & 9.06 \\ 
MBP & ILMN\_2398939 & rs8092433 & rs4890876 & 2 & MBP & 3 & 5.9 \\ 
NAPRT1 & ILMN\_1710752 & rs2123758 & rs3889129 & 1 & NAPRT1 & 80 & 7.36 \\ 
NCL & ILMN\_2121437 & rs7563453 & rs4973397 & 2 & NCL & 4 & 5.88 \\ 
PRMT2 & ILMN\_1675038 & rs2839372 & rs11701058 & 2 & PRMT2 & 39 & 7.07 \\ 
SNORD14A & ILMN\_1799381 & rs2634462 & rs6486334 & 2 & SNORD14A & 63 & 7.22 \\ 
TMEM149 & ILMN\_1786426 & rs807491 & rs7254601 & 1 & TMEM149 & 74 & 7.4 \\ 
TMEM149 & ILMN\_1786426 & rs8106959 & rs1843357 & 1 & TMEM149 & 148 & 9.71 \\ 
TMEM149 & ILMN\_1786426 & rs8106959 & rs2351458 & 1 & TMEM149 & 154 & 9.71 \\ 
TMEM149 & ILMN\_1786426 & rs8106959 & rs6718480 & 1 & TMEM149 & 146 & 9.71 \\ 
TMEM149 & ILMN\_1786426 & rs8106959 & rs6926382 & 1 & TMEM149 & 157 & 9.71 \\ 
TMEM149 & ILMN\_1786426 & rs8106959 & rs914940 & 1 & TMEM149 & 156 & 9.71 \\ 
TMEM149 & ILMN\_1786426 & rs8106959 & rs9509428 & 1 & TMEM149 & 160 & 9.71 \\ 
VASP & ILMN\_1743646 & rs1264226 & rs2276470 & 2 & VASP & 10 & 6.81 \\ 
RPL13 & ILMN\_2413278 & rs352935 & rs2965817 & 2 & RPL13 & 2 & 6.57 \\ 
TRA2A & ILMN\_1731043 & rs7776572 & rs11770192 & 2 & TRA2A & 7 & 6.84 \\ 
   \hline
\end{tabular}
\caption*{The $\lambda$ and type 1 error rates for the 30 (Bonferroni-correction) significant replicated pairs mentioned in Hemani \emph{et al}. P\_emp demotes the permutation empirical p-value}
\end{table}

@@

\begin{figure}[H]
\centering
\includegraphics[height=3in]{perm_vs_gwas.png}
\caption*{Figure | the relationship between the empirical p-values from the permutation and GWAS-based methods. It is unclear why there is this relationship. I've checked the results and code several times and believe this is correct.}
\end{figure}

>>>>

\documentclass[paper=a4, fontsize=11pt]{scrartcl}         % Article class of KOMA-script with 11pt font and a4 format
\usepackage[T1]{fontenc}
\usepackage{fourier}
\usepackage{float}
\usepackage{placeins}
\usepackage[english]{babel}                     % English language/hyphenation
\usepackage[protrusion=true,expansion=true]{microtype}        % Better typography
\usepackage{amsmath,amsfonts,amsthm}                % Math packages
\usepackage[pdftex]{graphicx}                   % Enable pdflatex
\usepackage{url}
\usepackage{multicol}
\usepackage{lscape}
\usepackage{parskip}
\usepackage{longtable}

@@

\begin{table}[ht]
\centering
\begin{tabular}{llllllll}
  \hline
 gene & probename & snp1 & snp2 & filter & gene.1 & nthreshold & P\_emp \\ 
  \hline
ADK & ILMN\_2358626 & rs2395095 & rs10824092 & 1 & ADK & 3 & 7.74 \\ 
ATP13A1 & ILMN\_2134224 & rs4284750 & rs873870 & 2 & ATP13A1 & 23 & 7.08 \\ 
C21ORF57 & ILMN\_1795836 & rs9978658 & rs11701361 & 2 & C21ORF57 & 6 & 5.65 \\ 
CSTB & ILMN\_1761797 & rs9979356 & rs3761385 & 2 & CSTB & 4 & 7.51 \\ 
CTSC & ILMN\_2242463 & rs7930237 & rs556895 & 1 & CTSC & 1 & 5.59 \\ 
FN3KRP & ILMN\_1652333 & rs898095 & rs9892064 & 2 & FN3KRP & 7 & 6.77 \\ 
GAA & ILMN\_2410783 & rs11150847 & rs12602462 & 2 & GAA & 9 & 6.91 \\ 
HNRPH1 & ILMN\_2101920 & rs6894268 & rs4700810 & 2 & HNRPH1 & 13 & 7.14 \\ 
LAX1 & ILMN\_1769782 & rs1891432 & rs10900520 & 2 & LAX1 & 5 & 6.64 \\ 
MBLN1 & ILMN\_2313158 & rs11981513 & rs13069559 & 1 & MBNL1 & 86 & 9.06 \\ 
MBLN1 & ILMN\_2313158 & rs16864367 & rs13079208 & 2 & MBNL1 & 79 & 7.22 \\ 
MBLN1 & ILMN\_2313158 & rs2030926 & rs13069559 & 1 & MBNL1 & 91 & 9.06 \\ 
MBLN1 & ILMN\_2313158 & rs218671 & rs13069559 & 1 & MBNL1 & 98 & 9.06 \\ 
MBLN1 & ILMN\_2313158 & rs2614467 & rs13069559 & 1 & MBNL1 & 95 & 9.06 \\ 
MBLN1 & ILMN\_2313158 & rs7710738 & rs13069559 & 1 & MBNL1 & 89 & 9.06 \\ 
MBP & ILMN\_2398939 & rs8092433 & rs4890876 & 2 & MBP & 3 & 5.9 \\ 
NAPRT1 & ILMN\_1710752 & rs2123758 & rs3889129 & 1 & NAPRT1 & 80 & 7.36 \\ 
NCL & ILMN\_2121437 & rs7563453 & rs4973397 & 2 & NCL & 4 & 5.88 \\ 
PRMT2 & ILMN\_1675038 & rs2839372 & rs11701058 & 2 & PRMT2 & 39 & 7.07 \\ 
SNORD14A & ILMN\_1799381 & rs2634462 & rs6486334 & 2 & SNORD14A & 63 & 7.22 \\ 
TMEM149 & ILMN\_1786426 & rs807491 & rs7254601 & 1 & TMEM149 & 74 & 7.4 \\ 
TMEM149 & ILMN\_1786426 & rs8106959 & rs1843357 & 1 & TMEM149 & 148 & 9.71 \\ 
TMEM149 & ILMN\_1786426 & rs8106959 & rs2351458 & 1 & TMEM149 & 154 & 9.71 \\ 
TMEM149 & ILMN\_1786426 & rs8106959 & rs6718480 & 1 & TMEM149 & 146 & 9.71 \\ 
TMEM149 & ILMN\_1786426 & rs8106959 & rs6926382 & 1 & TMEM149 & 157 & 9.71 \\ 
TMEM149 & ILMN\_1786426 & rs8106959 & rs914940 & 1 & TMEM149 & 156 & 9.71 \\ 
TMEM149 & ILMN\_1786426 & rs8106959 & rs9509428 & 1 & TMEM149 & 160 & 9.71 \\ 
VASP & ILMN\_1743646 & rs1264226 & rs2276470 & 2 & VASP & 10 & 6.81 \\ 
RPL13 & ILMN\_2413278 & rs352935 & rs2965817 & 2 & RPL13 & 2 & 6.57 \\ 
TRA2A & ILMN\_1731043 & rs7776572 & rs11770192 & 2 & TRA2A & 7 & 6.84 \\ 
   \hline
\end{tabular}
\caption*{The $\lambda$ and type 1 error rates for the 30 (Bonferroni-correction) significant replicated pairs mentioned in Hemani \emph{et al}. P\_emp demotes the p-value from the observed F-statistic (df1=4, df2=846) which corresponds to $n*4.44e^{-6}$ ranked test statistic from the ‘gwas’ analysis. If $n*4.4e^{-6} < 1$ then the top ranked F-stat was used.  }
\end{table}

@@

\begin{figure}[H]
\centering
\includegraphics[height=3in]{perm_vs_lambdaF.png}
\caption*{Figure | the relationship between the observed p values corrected for lambdaF, which was calculated from the GWAS-based analysis and the permutation empitical p-values}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[height=3in]{perm_vs_lambdaC.png}
\caption*{Figure | the relationship between the observed p values corrected for lambdaChisq, which was calculated from the GWAS-based analysis and the permutation empitical p-values}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[height=3in]{lambda.png}
\caption*{Figure | the relationship between the lambdaChisq and lambdaF from the GWAS-based analysis}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[height=4in]{TreeOfLife.png}
\caption*{Figure | This figure denotes the numbers of Probe by SNP pairs that pass verious thresholds and split on original filtering and relative positional information. All pairs that pass both the permutation empirical p value threshold of $4.48e-6$ and the $\lambda_F$ corrected threshold of $4.48e-6$ are summerized in the table \emph{datasig.csv} and \emph{datasig\_lite.csv}. The total number of paris in this table is 155}
\end{figure}
